### 2023-02-08 materials_methods.tex
Add missing citations

Genome quality impacts conclusions drawn from comparative genomic studies. \TODO{Juan, add citations.}
Genomes for model organisms often get refined over many iterations and achieve high quality with meticulously curated protein coding sequences.
In contrast, genomes for non-model organisms might only receive partial curation and typically have lower quality sequences and annotations.
These genomes often lack the amount of sequencing data needed to fix artifacts, including missing exons, erroneous mutations, and indels \citembe{jackman2018tigmint}.
FSTs and their powerful methods provide a well-suited framework to statistically align a sequence from a non-model organism against a sequence from a model organism.

>>>>

Genome quality impacts conclusions drawn from comparative genomic studies \citembethree{estimates_schneider_2009}{effect_fletcher_2010}{hubisz2011error}.
Genomes for model organisms often get refined over many iterations and achieve high quality with meticulously curated protein coding sequences.
In contrast, genomes for non-model organisms might only receive partial curation and typically have lower quality sequences and annotations.
These genomes often lack the amount of sequencing data needed to fix artifacts, including missing exons, erroneous mutations, and indels \citembe{jackman2018tigmint}.
FSTs and their powerful methods provide a well-suited framework to statistically align a sequence from a non-model organism against a sequence from a model organism.
